---
title: "Titanic Model"
author: "Yoshita Narang"
date: "2022-10-16"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction
Proposing the eminent Kaggle Titanic dataset in a Machine Learning competition. The purpose of my works are to use machine learning to create a model that predicts which passengers survived the Titanic shipwreck. Using R, I will implement this model using Data Science to depict accurate graphs and perform statistical analysis to determine survival rates as a binary (0 = did not survive & 1 = survived). 

```{r}
setwd("~/Library/CloudStorage/Box-Box/Playground Learning/Kaggle/Titanic_Disaster_Dataset")
titanic.train <- read.csv(file = "train.csv", 
                          stringsAsFactors = FALSE, 
                          header = TRUE, na.strings = "")
titanic.test <- read.csv(file = "test.csv", 
                          stringsAsFactors = FALSE, 
                          header = TRUE)
# titanic.train has column Cabin and Age that has many NA values 
# plot missingness map which shows the missing values

```
## Data Cleaning 

```{r}
# Creating new column & assigning all values to true 
titanic.train$IsTrainSet <- TRUE
# Creating new column & assigning all values to false 
titanic.test$IsTrainSet <- FALSE
# Test set lacks SURVIVED col, so ADD col
```
